---
title: "NFL 2020 Week 19"
author: "MAJ Daniel Baller"
date: "8/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r Loading Packages, include=FALSE}
library(tidyverse)
library(data.table)
library(formattable)
library(ggpubr)
library(ggrepel)
library(gt)
library(glue)
library(ggthemes)
library(hrbrthemes)
library(sparkline)
source("../Functions/functions2.R")
```

```{r Reading in our picks files, include=FALSE}
week_1 = read_csv("../CSV_Data_Files/2020 NFL Week 1.csv")
week_2 = read_csv("../CSV_Data_Files/2020 NFL Week 2.csv")
week_3 = read_csv("../CSV_Data_Files/2020 NFL Week 3.csv")
week_4 = read_csv("../CSV_Data_Files/2020 NFL Week 4.csv")
week_5 = read_csv("../CSV_Data_Files/2020 NFL Week 5.csv")
week_6 = read_csv("../CSV_Data_Files/2020 NFL Week 6.csv")
week_7 = read_csv("../CSV_Data_Files/2020 NFL Week 7.csv")
week_8 = read_csv("../CSV_Data_Files/2020 NFL Week 8.csv")
week_9 = read_csv("../CSV_Data_Files/2020 NFL Week 9.csv")
week_10 = read_csv("../CSV_Data_Files/2020 NFL Week 10.csv")
week_11 = read_csv("../CSV_Data_Files/2020 NFL Week 11.csv")
week_12 = read_csv("../CSV_Data_Files/2020 NFL Week 12.csv")
week_13 = read_csv("../CSV_Data_Files/2020 NFL Week 13.csv")
week_14 = read_csv("../CSV_Data_Files/2020 NFL Week 14.csv")
week_15 = read_csv("../CSV_Data_Files/2020 NFL Week 15.csv")
week_16 = read_csv("../CSV_Data_Files/2020 NFL Week 16.csv")
week_17 = read_csv("../CSV_Data_Files/2020 NFL Week 17.csv")
week_18 = read_csv("../CSV_Data_Files/2020 NFL Wild Card.csv")
week_19 = read_csv("../CSV_Data_Files/2020 NFL Divisional Round.csv")
cadet_wk1 = read_csv("../CSV_Data_Files/2020 NFL Week 1 MA206.csv")
cadet_wk2 = read_csv("../CSV_Data_Files/2020 NFL Week 2 MA206.csv")
cadet_wk3 = read_csv("../CSV_Data_Files/2020 NFL Week 3 MA206.csv")
cadet_wk4 = read_csv("../CSV_Data_Files/2020 NFL Week 4 MA206.csv")
cadet_wk5 = read_csv("../CSV_Data_Files/2020 NFL Week 5 MA206.csv")
cadet_wk6 = read_csv("../CSV_Data_Files/2020 NFL Week 6 MA206.csv")
cadet_wk7 = read_csv("../CSV_Data_Files/2020 NFL Week 7 MA206.csv")
cadet_wk8 = read_csv("../CSV_Data_Files/2020 NFL Week 8 MA206.csv")
cadet_wk9 = read_csv("../CSV_Data_Files/2020 NFL Week 9 MA206.csv")
cadet_wk10 = read_csv("../CSV_Data_Files/2020 NFL Week 10 MA206.csv")
cadet_wk11 = read_csv("../CSV_Data_Files/2020 NFL Week 11 MA206.csv")
cadet_wk12 = read_csv("../CSV_Data_Files/2020 NFL Week 12 MA206.csv")
cadet_wk13 = read_csv("../CSV_Data_Files/2020 NFL Week 13 MA206.csv")
cadet_wk14 = read_csv("../CSV_Data_Files/2020 NFL Week 14 MA206.csv")
cadet_wk15 = read_csv("../CSV_Data_Files/2020 NFL Week 15 MA206.csv")
cadet_wk16 = read_csv("../CSV_Data_Files/2020 NFL Week 16 MA206.csv")
cadet_wk17 = read_csv("../CSV_Data_Files/2020 NFL Week 17 MA206.csv")
cadet_wk18 = read_csv("../CSV_Data_Files/2020 NFL Wild Card MA206.csv")
cadet_wk19 = read_csv("../CSV_Data_Files/2020 NFL Divisional Round MA206.csv")

weeks = list(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19) #Setting the weeks #add in additional weeks
inst.picks = list(week_1, week_2, week_3, week_4, week_5, week_6, week_7, week_8,
                  week_9, week_10, week_11, week_12, week_13, week_14, week_15,
                  week_16, week_17, week_18, week_19) #add in the additional weeks
cdt.picks = list(cadet_wk1, cadet_wk2, cadet_wk3, cadet_wk4, cadet_wk5,
                 cadet_wk6, cadet_wk7, cadet_wk8, cadet_wk9, cadet_wk10,
                 cadet_wk11, cadet_wk12, cadet_wk13, cadet_wk14, cadet_wk15,
                 cadet_wk16, cadet_wk17, cadet_wk18, cadet_wk19) #add in the additional weeks
```

```{r read in scores clean data, include=FALSE}
Scores = read_csv("../CSV_Data_Files/NFL_Scores_19.csv") 

#Cleaning the data and getting a total list of winners
Scores = cleaning2(Scores)
Scores %>% as.data.frame()

#creating a list of winners for each week
winners = map(weeks, weekly_winners)

#creating a vector of this weeks winners
this_week = pull(winners[[length(winners)]])  

#Getting the number of games for each week
weekly_number_of_games = map_dbl(weeks, week_number_games)
```

## Instructor Group Predictions

```{r Group Predictions, include=FALSE}
#Creating the list of everyones predictions each week.
games = map(inst.picks, games_fn)

#Creating the prediction table.  
pred_table = map(games, pred_table_fn)

#Adding who won to the predictions
with_winners = map2(pred_table, winners, adding_winners)

#Creating results for each week.
results = map2(with_winners,weekly_number_of_games, results_fn)

```


```{r Displaying Group Results, echo=FALSE, out.height="80%"}
#Displaying the group results

group_table = results[[length(results)]] %>% 
  gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("This Week's Predictions"),
    subtitle = md(glue("Week {length(results)}"))
    ) %>% 
   tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="No"
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="Yes"
    )) %>% 
  tab_options(
    data_row.padding = px(3)
   )

group_table
```

```{r saving group table, include=FALSE}
gtsave(group_table, glue::glue("../Tables_and_Plots/Week_{length(weeks)}/Group_Table_Week_{length(weeks)}.png"))
```

```{r Weekly and season Group Results, include=FALSE}
# Printing the weekly and season win percentage     

#how many games correct, incorrect, and not picked each week
weekly_group_correct = map(results, weekly_group_correct_fn)  

#how many games were picked each week
weekly_games_picked = map2(weekly_group_correct, weekly_number_of_games, weekly_games_picked_fn)

#Calculating the number of correct picks for each week
weekly_group_correct_picks = map(weekly_group_correct, weekly_group_correct_picks_fn)

#Calculating weekly win percentage
weekly_win_percentage = map2(weekly_group_correct_picks, weekly_games_picked, weekly_win_percentage_fn)

#Calculating season win percentage
season_win_percentage = round(sum(unlist(weekly_group_correct_picks))/sum(unlist(weekly_games_picked)),4)

#Calculating number of games picked this season
season_games = sum(unlist(weekly_games_picked))

#calculating season wins
season_wins = sum(unlist(weekly_group_correct_picks))

#calculating the number of people who picked this week
Total = dim(data)[1]

 #Need to fix
# `r paste("CBS Sports win percentage for the week is", CBS, sep = " ") `
```
 `r paste("Our win percentage for the week is", weekly_win_percentage[[length(weekly_win_percentage)]], sep = " ") `
 
 `r paste("Our season win percentage so far is", season_win_percentage, sep = " ") `
 
 `r paste("Games picked this season", season_games, sep = " ") `
 
 `r paste("Correct Games this season", season_wins, sep = " ") `
 
 `r paste(Total, "predictions this week", sep = " ") `
```{r plotting group results, include=FALSE}
#Previous Weeks
group_season_for_plotting = unlist(weekly_win_percentage) %>% as.data.frame() %>% 
  rename(`Win Percentage` = ".") %>% 
  add_column(Week = unlist(weeks))
```

```{r Plotting the group results, echo=FALSE}
group_plot = group_season_for_plotting %>% 
ggplot(aes(x = as.factor(Week), y = `Win Percentage`))+
  geom_point()+
  geom_path(aes(x = Week))+
  geom_text(aes(label=`Win Percentage`),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  xlab("NFL Week") + 
  ylab("Correct Percentage")+
  ggtitle("Weekly Group Correct Percentage")+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, size = 18))

group_plot
```

```{r saving group plot, include=FALSE}
ggsave(glue("../Tables_and_Plots/Week_{length(weeks)}/Group_Plot_Week_{length(weeks)}.png"),plot = group_plot, scale = 2)
```

```{r individual results, include=FALSE}
#Creating a list of individual results for each week.
weekly_indiv = pmap(list(inst.picks, winners, weeks), indiv_weekly_pred)

#Combining each week into one dataframe and calculating percentage Correct for this week.  
full_season = weekly_indiv %>% reduce(full_join, by = "Name") %>% 
  mutate(Percent = round(pull(.[,ncol(.)]/weekly_games_picked[[length(weekly_games_picked)]]),4)) 

#Creating a dataframe with only the weekly picks
a = full_season %>% select(starts_with("Week"))

#Creating a vector of how many weeks each person picked over the season
tot_week = NULL
help = NULL
for (i in 1:dim(a)[1]){
  for(j in 1:length(a)){
    help[j] = ifelse(is.na(a[i,j])==T,0,1)
    tot_week[i] = sum(help)
  }
}

#Creating a vector of how many games each person picked over the season
tot_picks= NULL
help = NULL
for (i in 1:dim(a)[1]){
  for(j in 1:length(a)){
    help[j] = unlist(weekly_games_picked)[j]*ifelse(is.na(a[i,j])==T,0,1)
    tot_picks[i] = sum(help)
  }
}

#Creatign a vector of how many games each person picked correct over the season
tot_correct = NULL
help = NULL
for (i in 1:dim(a)[1]){
  tot_correct[i] = sum(a[i,], na.rm = T)
}

#adding how many weeks each person picked, season correct percentage, and adjusted season percentag to the data frame and sorting the data
indiv_disp = full_season %>% add_column(`Weeks Picked` = tot_week) %>%
  add_column(tot_correct)%>%
  add_column(tot_picks)%>%
  mutate(`Season Percent` = round(tot_correct/tot_picks,4))%>%
  mutate(`Adj Season Percent` = round(`Season Percent`*(tot_week/length(a)),4)) %>%
  select(-tot_correct, -tot_picks) %>%
  arrange(desc(Percent), desc(`Season Percent`)) %>%
  mutate(Percent = ifelse(is.na(Percent)==T, 0, Percent))
```

## Individual Predictions

```{r individual percentages, include=FALSE}
#Calculating individual percentages for each week.
weekly_indiv_percent = map2(weekly_indiv, weekly_games_picked, indiv_percent) %>% reduce(full_join, by = "Name")

weekly_indiv_percent_plot = weekly_indiv_percent %>% 
  pivot_longer(cols = starts_with("Week"), names_to = "Week", values_to = "Percent")%>%
  mutate(Percent = ifelse(is.na(Percent)==T, 0, Percent)) %>% 
  mutate(Week = as.factor(Week))

levels = NULL
for(i in 1:length(weeks)){
  levels[i] = glue("Week {i}")  
}

weekly_indiv_percent_plot = weekly_indiv_percent_plot %>%
  mutate(Week = factor(Week, levels))
```

```{r sparklines, include=FALSE}
#adding sparklines
plot_group = function(name, df){
  plot_object = 
    ggplot(data = df,
           aes(x = as.factor(Week), y=Percent, group = 1))+
    geom_path(size = 7)+
    scale_y_continuous(limits = c(0,1))+
    theme_void()+
    theme(legend.position = "none")
  return(plot_object)
}

sparklines = 
  weekly_indiv_percent_plot %>% 
  group_by(Name) %>% 
  nest() %>% 
  mutate(plot = map2(Name, data, plot_group)) %>% 
  select(-data)
  
indiv_disp_2 = indiv_disp %>% 
  inner_join(sparklines, by = "Name") %>% 
  mutate(`Season Trend` = NA)
```

```{r Printing Individual Table2, echo=FALSE}
# Printing the individual Table
indiv_table = indiv_disp_2 %>% gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("Individual Results"),
    subtitle = md(glue("Week {length(weeks)}"))
    ) %>% 
   tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(Percent),
      rows = Percent<.5
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(Percent),
      rows = Percent>.5
    )) %>% 
     tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(`Season Percent`),
      rows = `Season Percent`<.5
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(`Season Percent`),
      rows = `Season Percent`>.5
    ))%>% 
     tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(`Adj Season Percent`),
      rows = `Adj Season Percent`<.5
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(`Adj Season Percent`),
      rows = `Adj Season Percent`>.5
    )) %>% 
  tab_options(
    container.width = pct(100),
    data_row.padding = px(1)
   ) %>%
    tab_spanner(
    label = "Weekly # Correct",
    columns = starts_with(c("Week "))
  ) %>% 
  text_transform(
    locations = cells_body(vars(`Season Trend`)),
    fn = function(x){
      map(indiv_disp_2$plot, ggplot_image, height = px(30), aspect_ratio = 4)
                 }) %>%
  cols_hide(vars(plot))

indiv_table
```
 `r paste("Congrats",indiv_disp$Name[which(indiv_disp$Percent == max(indiv_disp$Percent))],"for having the best picks this week, with a correct percentage of", max(indiv_disp$Percent), sep = " ") `

```{r saving individual table, include=FALSE}
gtsave(indiv_table, glue::glue("../Tables_and_Plots/Week_{length(weeks)}/Individual_Table_Week_{length(weeks)}.png"), zoom = 2)
```

```{r instructor formattable, echo=FALSE}
improvement_formatter <- 
  formatter("span", 
            style = x ~ style(
              font.weight = "bold", 
              color = ifelse(x > .5, "green", ifelse(x < .5, "red", "black"))),
             x ~ icontext(ifelse(x == max(x), "star", ""), x))

indiv_disp_3 = indiv_disp_2 %>% select(-plot)
indiv_disp_3$`Season Trend` = apply(indiv_disp_3[,2:(1+length(weeks))], 1, FUN = function(x) as.character(htmltools::as.tags(sparkline(as.numeric(x), type = "line", chartRangeMin = 0, chartRangeMax = 1, fillColor = "white"))))

out = as.htmlwidget(formattable(indiv_disp_3, 
                                align = c("l", rep("c", NROW(indiv_disp_3)-1)),
              list(`Season Percent` = color_bar("#FA614B"),
              `Season Percent`= improvement_formatter,
              `Adj Season Percent`= improvement_formatter)))
              
out$dependencies = c(out$dependencies, htmlwidgets:::widget_dependencies("sparkline", "sparkline"))

out
```

```{r Plotting individual results over the season, eval=FALSE, include=FALSE, out.width="100%"}
#Creating the individual plot.  
weekly_indiv_percent %>% 
  pivot_longer(cols = starts_with("Week"), names_to = "Week", values_to = "Percent") %>% 
  mutate(Percent = ifelse(is.na(Percent)==T, 0, Percent)) %>% 
  #group_by(Name) %>% 
  ggplot(aes(x = as.factor(Week), y = Percent, color = Name))+
  geom_point()+
  geom_line(aes(x = as.factor(Week), y = Percent, color = Name, 
                group = Name))+
  geom_text_repel(aes(label=Name),hjust=0, vjust=0, size = 3)+
  #geom_text(aes(label=Percent),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week", 
       y = "Correct Percentage", 
       title = "Weekly Individual Correct Percentage")+
  theme_classic()+
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 18))
```

```{r Plotting individual results over the season2, echo=FALSE, out.width = "100%"}
#Creating the individual plot.  
indiv_plot = weekly_indiv_percent_plot %>% 
  ggplot(aes(x = factor(Week), y = Percent, color = Name))+
  geom_point()+
  geom_path(aes(x = as.factor(Week), y = Percent, color = Name, 
                group = Name))+
  geom_text_repel(aes(label=round(Percent,3)),hjust=0.5, vjust=2, size = 3)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week", 
       y = "Correct Percentage", 
       title = "Weekly Individual Correct Percentage")+
  facet_wrap(~Name)+
  theme_classic()+
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 18),
        axis.text.x=element_text(angle =45, vjust = 1, hjust = 1))

indiv_plot
```

```{r saving individual plot, include=FALSE}
ggsave(glue("../Tables_and_Plots/Week_{length(weeks)}/Individual_Plot_Week_{length(weeks)}.png"),plot = indiv_plot, scale = 3)
```

## MA206 Group Predictions

```{r Cadet Group Predictions, include=FALSE}
#Creating the list of everyones predictions each week.
c_games = map(cdt.picks, games_fn)

#Creating the prediction table.  
c_pred_table = map(c_games, pred_table_fn)

#Adding who won to the predictions
c_with_winners = map2(c_pred_table, winners, adding_winners)

#Creating results for each week.
c_results = map2(c_with_winners,weekly_number_of_games, c_results_fn)
```

```{r Printing Cadet Group Prediction Table, echo=FALSE}
#Displaying the group results
c_group_table = c_results[[length(c_results)]] %>% 
  gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("This Week's MA206 Predictions"),
    subtitle = md(glue("Week {length(results)}"))
    ) %>% 
   tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="No"
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="Yes"
    ))%>% 
  tab_options(
    data_row.padding = px(3)
   )

c_group_table
```

```{r saving cadet group table, include=FALSE}
gtsave(c_group_table, glue::glue("../Tables_and_Plots/Week_{length(weeks)}/Cadet_Group_Table_Week_{length(weeks)}.png"))
```

```{r Cadet Weekly and season Group Results, include=FALSE}
# Printing the weekly and season win percentage     

#how many games correct, incorrect, and not picked each week
c_weekly_group_correct = map(c_results, weekly_group_correct_fn)  

#how many games were picked each week
c_weekly_games_picked = map2(c_weekly_group_correct, weekly_number_of_games, weekly_games_picked_fn)

#Calculating the number of correct picks for each week
c_weekly_group_correct_picks = map(c_weekly_group_correct, weekly_group_correct_picks_fn)

#Calculating weekly win percentage
c_weekly_win_percentage = map2(c_weekly_group_correct_picks, c_weekly_games_picked, weekly_win_percentage_fn)

#Calculating season win percentage
c_season_win_percentage = round(sum(unlist(c_weekly_group_correct_picks))/sum(unlist(c_weekly_games_picked)),4)

#Calculating number of games picked this season
c_season_games = sum(unlist(c_weekly_games_picked))

#calculating season wins
season_wins = sum(unlist(weekly_group_correct_picks))
```

```{r Data for MA206 group results, include=FALSE}
#Previous Weeks
c_group_season_for_plotting = unlist(c_weekly_win_percentage) %>% as.data.frame() %>% 
  rename(`Win Percentage` = ".") %>% 
  add_column(Week = unlist(weeks))
```

```{r Plotting MA206 group results, echo=FALSE}
c_group_plot = c_group_season_for_plotting %>% 
ggplot(aes(x = as.factor(Week), y = `Win Percentage`))+
  geom_point()+
  geom_path(aes(x = Week))+
  geom_text(aes(label=`Win Percentage`),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week", 
       y = "Correct Percentage", 
       title = "Weekly MA206 Group Correct Percentage", 
       caption = glue::glue("Best week is Week {c_group_season_for_plotting$Week[which(c_group_season_for_plotting$`Win Percentage`==max(c_group_season_for_plotting$`Win Percentage`))]}"))+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, size = 18))

c_group_plot
```

```{r saving cadet group plot, include=FALSE}
ggsave(glue("../Tables_and_Plots/Week_{length(weeks)}/Cadet_Group_Plot_Week_{length(weeks)}.png"),plot = c_group_plot, scale = 2)
```

# Cadet Individual Results
```{r cdt individual results, include=FALSE}
#Creating a list of individual results for each week.
c_weekly_indiv = pmap(list(cdt.picks, winners, weeks), indiv_weekly_pred)

#Combining each week into one dataframe and calculating percentage Correct for this week.  
c_full_season = c_weekly_indiv %>% reduce(full_join, by = "Name") %>% 
  mutate(Percent = round(pull(.[,ncol(.)]/weekly_games_picked[[length(weekly_games_picked)]]),4)) 

#Creating a dataframe with only the weekly picks
c_a = c_full_season %>% select(starts_with("Week"))

#Creating a vector of how many weeks each person picked over the season
c_tot_week = NULL
c_help = NULL
for (i in 1:dim(c_a)[1]){
  for(j in 1:length(c_a)){
    c_help[j] = ifelse(is.na(c_a[i,j])==T,0,1)
    c_tot_week[i] = sum(c_help)
  }
}

#Creating a vector of how many games each person picked over the season
c_tot_picks= NULL
c_help = NULL
for (i in 1:dim(c_a)[1]){
  for(j in 1:length(c_a)){
    c_help[j] = unlist(weekly_games_picked)[j]*ifelse(is.na(c_a[i,j])==T,0,1)
    c_tot_picks[i] = sum(c_help)
  }
}

#Creatign a vector of how many games each person picked correct over the season
c_tot_correct = NULL
c_help = NULL
for (i in 1:dim(c_a)[1]){
  c_tot_correct[i] = sum(c_a[i,], na.rm = T)
}

#adding how many weeks each person picked, season correct percentage, and adjusted season percentag to the data frame and sorting the data
c_indiv_disp = c_full_season %>% 
  add_column(`Weeks Picked` = c_tot_week) %>%
  add_column(c_tot_correct)%>%
  add_column(c_tot_picks)%>%
  mutate(`Season Percent` = round(c_tot_correct/c_tot_picks,4))%>%
  mutate(`Adj Season Percent` = round(`Season Percent`*(c_tot_week/length(c_a)),4)) %>%
  select(-c_tot_correct, -c_tot_picks) %>%
  arrange(desc(Percent), desc(`Season Percent`)) %>%
  mutate(Percent = ifelse(is.na(Percent)==T, 0, Percent))
```

```{r cdt individual percentages, include=FALSE}
#Calculating  individual percentages for each week.
c_weekly_indiv_percent = map2(c_weekly_indiv, weekly_games_picked, indiv_percent) %>% reduce(full_join, by = "Name")

c_weekly_indiv_percent_plot = c_weekly_indiv_percent %>% 
  pivot_longer(cols = starts_with("Week"), names_to = "Week", values_to = "Percent") %>% 
  mutate(Percent = ifelse(is.na(Percent)==T, 0, Percent))

c_weekly_indiv_percent_plot = c_weekly_indiv_percent_plot %>%
  mutate(Week = factor(Week, levels))
```

```{r cadet sparklines, include=FALSE}
#adding sparklines
c_sparklines = 
  c_weekly_indiv_percent_plot %>% 
  group_by(Name) %>% 
  nest() %>% 
  mutate(plot = map2(Name, data, plot_group)) %>% 
  select(-data)
  
c_indiv_disp_2 = c_indiv_disp %>% 
  inner_join(c_sparklines, by = "Name") %>% 
  mutate(`Season Trend` = NA)
```

```{r Printing Individual Cdt Table, echo=FALSE}
# Printing the individual Table
c_indiv_table = c_indiv_disp_2 %>% 
  gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("MA206 Individual Results"),
    subtitle = md(glue("Week {length(weeks)}"))
    ) %>% 
   tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(Percent),
      rows = Percent<.5
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(Percent),
      rows = Percent>.5
    )) %>% 
     tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(`Season Percent`),
      rows = `Season Percent`<.5
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(`Season Percent`),
      rows = `Season Percent`>.5
    ))%>% 
     tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(`Adj Season Percent`),
      rows = `Adj Season Percent`<.5
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(`Adj Season Percent`),
      rows = `Adj Season Percent`>.5
    ))%>% 
  tab_options(
    data_row.padding = px(3)
   )%>% 
    tab_spanner(
    label = "Weekly # Correct",
    columns = starts_with(c("Week "))
  )%>% 
  text_transform(
    locations = cells_body(vars(`Season Trend`)),
    fn = function(x){
      map(c_indiv_disp_2$plot, ggplot_image, height = px(30), aspect_ratio = 4)
                 }) %>%
  cols_hide(vars(plot))

c_indiv_table
#below may not work if a tie
```
 `r paste("Congrats",c_indiv_disp$Name[which(c_indiv_disp$Percent == max(c_indiv_disp$Percent))],"for having the best cadet picks this week, with a correct percentage of", max(c_indiv_disp$Percent), sep = " ") `

```{r saving cadet individual table, include=FALSE}
gtsave(c_indiv_table, glue::glue("../Tables_and_Plots/Week_{length(weeks)}/Cadet_Individual_Table_Week_{length(weeks)}.png"))
```

```{r cadet formattable, echo=FALSE}
c_indiv_disp_3 = c_indiv_disp_2 %>% select(-plot)
c_indiv_disp_3$`Season Trend` = apply(c_indiv_disp_3[,2:(1+length(weeks))], 1, FUN = function(x) as.character(htmltools::as.tags(sparkline(as.numeric(x), type = "line", chartRangeMin = 0, chartRangeMax = 1, fillColor = "white"))))

c_out = as.htmlwidget(formattable(c_indiv_disp_3, 
                                align = c("l", rep("c", NROW(c_indiv_disp_3)-1)),
              list(`Season Percent` = color_bar("#FA614B"),
              `Season Percent`= improvement_formatter,
              `Adj Season Percent`= improvement_formatter)))
              
c_out$dependencies = c(c_out$dependencies, htmlwidgets:::widget_dependencies("sparkline", "sparkline"))

c_out
```


```{r Plotting individual Cdt results over the season2, echo=FALSE}
#Creating the individual plot.  
c_indiv_plot = c_weekly_indiv_percent_plot %>% 
  ggplot(aes(x = as.factor(Week), y = Percent, color = Name))+
  geom_point()+
  geom_line(aes(x = as.factor(Week), y = Percent, color = Name, 
                group = Name))+
  geom_text_repel(aes(label=round(Percent,4)),hjust=.5, vjust=2, size = 3)+
  #geom_text(aes(label=Percent),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week",
       y = "Correct Percentage", 
       title = "Weekly MA206 Individual Correct Percentage")+
  theme_classic()+
  facet_wrap(~Name)+
#  scale_x_discrete(guide = guide_axis(n.dodge = 2))+
  theme(legend.position = "none",
    plot.title = element_text(hjust = 0.5, size = 18),
    axis.text.x=element_text(angle =45, vjust = 1, hjust = 1))

c_indiv_plot
```

```{r saving cadet indiv plot, include=FALSE}
ggsave(glue("../Tables_and_Plots/Week_{length(weeks)}/Cadet_Individual_Plot_Week_{length(weeks)}.png"),plot = c_indiv_plot, scale = 3)
```

## Combined cadet and instructor prediction
```{r Combined Cadet and Instructor Predictions, include=FALSE}
#Combining inst and cadet picks
comb_picks = map2(inst.picks, cdt.picks, comb_picks_fn)

#Creating the list of Combined predictions each week.
comb_games = map(comb_picks, games_fn)

#Creating the Combined prediction table.  
comb_pred_table = map(comb_games, pred_table_fn)

#Adding who won to the predictions
comb_with_winners = map2(comb_pred_table, winners, adding_winners)

#Creating Combined results for each week.
comb_results = map2(comb_with_winners,weekly_number_of_games, comb_results_fn)
```

```{r Printing Combined Prediction Results, echo=FALSE}
#Displaying the Combined results

comb_table = comb_results[[length(comb_results)]] %>% 
  gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("This Week's Combined Cadet and Instructor Predictions"),
    subtitle = md(glue("Week {length(results)}"))
    ) %>% 
   tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="No"
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="Yes"
    ))%>% 
  tab_options(
    data_row.padding = px(3)
   )
comb_table
```

```{r saving combined table, include=FALSE}
gtsave(comb_table, glue::glue("../Tables_and_Plots/Week_{length(weeks)}/Combined_Table_Week_{length(weeks)}.png"))
```

```{r Combined Results over season, include=FALSE}
#how many games correct, incorrect, and not picked each week
comb_weekly_group_correct = map(comb_results, weekly_group_correct_fn)  

#how many games were picked each week
comb_weekly_games_picked = map2(comb_weekly_group_correct, weekly_number_of_games, weekly_games_picked_fn)

#Calculating the number of correct picks for each week
comb_weekly_group_correct_picks = map(comb_weekly_group_correct, weekly_group_correct_picks_fn)

#Calculating weekly win percentage
comb_weekly_win_percentage = map2(comb_weekly_group_correct_picks, comb_weekly_games_picked, weekly_win_percentage_fn)

#Calculating season win percentage
comb_season_win_percentage = round(sum(unlist(comb_weekly_group_correct_picks))/sum(unlist(weekly_games_picked)),4)

#Calculating number of games picked this season
comb_season_games = sum(unlist(comb_weekly_games_picked))

#calculating season wins
comb_season_wins = sum(unlist(comb_weekly_group_correct_picks))

# #calculating combined weekly win percentage
# comb_weekly_win_percentage = map2(weekly_group_correct_picks, weekly_games_picked, weekly_win_percentage_fn)

#calculating the number of people who picked this week
comb_Total = dim(comb_picks[[length(comb_picks)]])[1]

comb_season_for_plotting = unlist(comb_weekly_win_percentage) %>% as.data.frame() %>% 
  rename(`Win Percentage` = ".") %>% 
  add_column(Week = unlist(weeks))
```

```{r Plotting the Combined group results, echo=FALSE}
comb_plot = comb_season_for_plotting %>% 
ggplot(aes(x = as.factor(Week), y = `Win Percentage`))+
  geom_point()+
  geom_path(aes(x = Week))+
  geom_text(aes(label=`Win Percentage`),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week", 
       y = "Correct Percentage", 
       title = "Weekly Combined Correct Percentage", 
       caption = glue::glue("Best week is Week {comb_season_for_plotting$Week[which(comb_season_for_plotting$`Win Percentage`==max(comb_season_for_plotting$`Win Percentage`))]}"))+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, size = 18))

comb_plot
```

```{r saving combined plot, include=FALSE}
ggsave(glue("../Tables_and_Plots/Week_{length(weeks)}/Combined_Plot_Week_{length(weeks)}.png"),plot = comb_plot, scale = 2)
```

 `r paste("Our combined win percentage for the week is", comb_weekly_win_percentage[[length(comb_weekly_win_percentage)]], sep = " ") `
 
 `r paste("Our season combined win percentage so far is", comb_season_win_percentage, sep = " ") `
 
 `r paste(comb_Total, "total predictions this week", sep = " ") `
 

```{r matched picks, include=FALSE}
#Finding where inst and Cadet predictions match
matched = map2(results, c_results, matched_fn)
```

```{r Printing matched results, echo=FALSE}
matched_table = matched[[length(matched)]] %>% 
  gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("This Week's Matched Cadet and Instructor Predictions"),
    subtitle = md(glue("Week {length(results)}"))
    ) %>% 
   tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="No"
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="Yes"
    ))%>% 
  tab_options(
    data_row.padding = px(3)
   )

matched_table
```

```{r saving matched table, include=FALSE}
gtsave(matched_table, glue::glue("../Tables_and_Plots/Week_{length(weeks)}/Matched_Table_Week_{length(weeks)}.png"))
```

```{r include=FALSE}
matched_per = map(matched, matched_percent_fn) %>% unlist() %>% as.data.frame() 

matched_season_percent_for_plotting = matched_per %>% 
  mutate(`Win Percentage` = matched_per[,1]) %>% 
  select(`Win Percentage`) %>% 
  add_column(Week = unlist(weeks)) 
```

```{r Plotting matched percent, echo=FALSE}
matched_plot = matched_season_percent_for_plotting %>% 
  ggplot(aes(x = as.factor(Week), y = `Win Percentage`))+
  geom_point()+
  geom_path(aes(x = Week))+
  geom_text(aes(label=`Win Percentage`),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week", 
       y = "Correct Percentage", 
       title = "Weekly Matched Correct Percentage", 
       caption = glue::glue("Best week is Week {comb_season_for_plotting$Week[which(comb_season_for_plotting$`Win Percentage`==max(comb_season_for_plotting$`Win Percentage`))]}"))+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, size = 18))

matched_plot
```

```{r saving matched plot, include=FALSE}
ggsave(glue("../Tables_and_Plots/Week_{length(weeks)}/Matched_Plot_Week_{length(weeks)}.png"),plot = matched_plot, scale = 3)
```

`r paste("Our matched win percentage for the week is", matched_per$Percent[length(matched_per$Percent)], sep = " ") `


```{r pregame, eval=FALSE, include=FALSE}
#Predictions for the week

#Creating the list of everyones predictions each week.
games = map(inst.picks, games_fn)

#Creating the prediction table.  
pred_table = map(games, pred_table_fn)

#Printing table of instructor predictions
pred_table[[length(pred_table)]] %>% mutate(Game = row_number()) %>% 
  rename(`Votes For` = votes_for, `Votes Against` = votes_against) %>% 
  gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("This Week's Predictions"),
    subtitle = md(glue("Week {length(weeks)}"))
    ) %>% 
   tab_options(
    data_row.padding = px(3)
   )

#Creating the list of everyones predictions each week.
c_games = map(cdt.picks, games_fn)

#Creating the prediction table.  
c_pred_table = map(c_games, pred_table_fn)

#Printing table of Cadet predictions
c_pred_table[[length(pred_table)]] %>% mutate(Game = row_number()) %>% 
  rename(`Votes For` = votes_for, `Votes Against` = votes_against) %>% 
  gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("This Week's Cadet Predictions"),
    subtitle = md(glue("Week {length(weeks)}"))
    ) %>% 
   tab_options(
    data_row.padding = px(3)
   )

```

```{r echo=FALSE}
group_season_for_plotting %>% add_column(Picks = "Instructors") %>% 
  rbind(c_group_season_for_plotting %>% add_column(Picks = "Cadets")) %>% 
  rbind(comb_season_for_plotting %>% add_column(Picks = "Combined")) %>% 
  rbind(matched_season_percent_for_plotting %>% add_column(Picks = "Matched")) %>% 
  ggplot(aes(x = as.factor(Week), y = `Win Percentage`, color = Picks))+
  geom_point()+
  geom_path(aes(x = Week))+
  geom_text_repel(aes(label=`Win Percentage`),hjust=0, vjust=0, size = 3)+
  #geom_text(aes(label=`Win Percentage`),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week", 
       y = "Correct Percentage",
       title = "Weekly Matched Correct Percentage")+
  theme_clean()+
  theme(plot.title = element_text(hjust = 0.5, size = 18),
        legend.position = "right")
```



