---
title: "NFL 2020 Week 3"
author: "MAJ Daniel Baller"
date: "8/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

```{r Loading Packages, include=FALSE}
library(tidyverse)
library(data.table)
library(formattable)
library(ggpubr)
library(ggrepel)
library(gt)
library(glue)
library(ggthemes)
library(hrbrthemes)
source("../Functions/functions2.R")
```

```{r Reading in our picks files, include=FALSE}
week_1 = read_csv("../CSV_Data_Files/2020 NFL Week 1.csv")
week_2 = read_csv("../CSV_Data_Files/2020 NFL Week 2.csv")
week_3 = read_csv("../CSV_Data_Files/2020 NFL Week 3.csv")
cadet_wk1 = read_csv("../CSV_Data_Files/2020 NFL Week 1 MA206.csv")
cadet_wk2 = read_csv("../CSV_Data_Files/2020 NFL Week 2 MA206.csv")
cadet_wk3 = read_csv("../CSV_Data_Files/2020 NFL Week 3 MA206.csv")

weeks = list(1,2,3) #Setting the weeks #add in additional weeks
inst.picks = list(week_1, week_2, week_3) #add in the additional weeks
cdt.picks = list(cadet_wk1, cadet_wk2, cadet_wk3) #add in the additional weeks
```

```{r read in scores clean data, include=FALSE}
Scores = read_csv("../CSV_Data_Files/NFL_Scores_3.csv") #%>% janitor::clean_names()
#Scores = read_csv("../CSV_Data_Files/NFL_Scores_12.csv") #%>% janitor::clean_names()

#Cleaning the data and getting a total list of winners
#Scores = cleaning(Scores)
Scores = cleaning2(Scores)

#creating a list of winners for each week
winners = map(weeks, weekly_winners)

#creating a vector of this weeks winners
this_week = pull(winners[[length(winners)]])  

#Getting the number of games for each week
weekly_number_of_games = map_dbl(weeks, week_number_games)
```

```{r eval=FALSE, include=FALSE}
wk1_FPI = c("Las Vegas Raiders", "Baltimore Ravens", "Chicago Bears", "Minisota Vikings","Buffalo Bills", "Seattle Seahawks",
            "New England Patriots","Indianapolis Colts", "Philidelphia Eagles", "Las Angeles Chargers", "New Orleans Saints", "San Fransisco 49ers", "Los Angeles Rams", "Pittsburgh Steelers", "Denver Broncos")
```


```{r number of games and CBS, message=FALSE, warning=FALSE, include=FALSE}
CBSsports = c("Jacksonville Jaguars","Buffalo Bills","Philidelphia Eagles","New England Patriots","Minnesota Vikings","Baltimore Ravens","Atlanta Falcons","Green Bay Packers","Dallas Cowboys","Tampa Bay Buccaneers","Carolina Panthers","San Francisco 49ers","Seattle Seahawks","Los Angeles Chargers","Los Angeles Rams","Chicago Bears")

wk1_CBSsports = c("Green Bay Packers","Atlanta Falcons","Miami Dolphins","New York Jets","Kansas City Chiefs","Carolina Panthers","Cleveland Browns","Philadelphia Eagles","Seattle Seahawks","Indianapolis Colts","Arizona Cardinals","Dallas Cowboys","Tampa Bay Buccaneers","Pittsburgh Steelers","New Orleans Saints","Oakland Raiders")

wk2_CBSsports = c("Carolina Panthers","Baltimore Ravens","Dallas Cowboys","Indianapolis Colts","Seattle Seahawks","Buffalo Bills","Cincinnati Bengals","Los Angeles Chargers","Green Bay Packers","Houston Texans","New England Patriots","Kansas City Chiefs","Los Angeles Rams","Chicago Bears","Philadelphia Eagles","Cleveland Browns")

#List of CBS Picks
CBS_tot = list(wk1_CBSsports, wk2_CBSsports, CBSsports)
#Is each pick correct
CBS = sum(ifelse(this_week == CBS_tot[[length(CBS_tot)]], 1, 0))/length(this_week)

#CBS = sum(experts)/length(this_week)
#CBS_weekly_winners = pmap(winners, CBS_tot, weeks, CBS_weekly)
#CBS_weekly_winners[[2]]

```

## Instructor Group Predictions

```{r Group Predictions, include=FALSE}
#Creating the list of everyones predictions each week.
games = map(inst.picks, games_fn)

#Creating the prediction table.  
pred_table = map(games, pred_table_fn)

#Adding who won to the predictions
with_winners = map2(pred_table, winners, adding_winners)

#Creating results for each week.
results = map2(with_winners,weekly_number_of_games, results_fn)
```


```{r Displaying Group Results, echo=FALSE, out.height="80%"}
#Displaying the group results

results[[length(results)]] %>% gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("This Week's Predictions"),
    subtitle = md(glue("Week {length(results)}"))
    ) %>% 
   tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="No"
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="Yes"
    )) %>% 
  tab_options(
    data_row.padding = px(3)
   )
```

```{r Weekly and season Group Results, include=FALSE}
# Printing the weekly and season win percentage     

#how many games correct, incorrect, and not picked each week
weekly_group_correct = map(results, weekly_group_correct_fn)  

#how many games were picked each week
weekly_games_picked = map2(weekly_group_correct, weekly_number_of_games, weekly_games_picked_fn)

#Calculating the number of correct picks for each week
weekly_group_correct_picks = map(weekly_group_correct, weekly_group_correct_picks_fn)

#Calculating weekly win percentage
weekly_win_percentage = map2(weekly_group_correct_picks, weekly_games_picked, weekly_win_percentage_fn)

#Calculating season win percentage
season_win_percentage = round(sum(unlist(weekly_group_correct_picks))/sum(unlist(weekly_games_picked)),4)

#Calculating number of games picked this season
season_games = sum(unlist(weekly_games_picked))

#calculating season wins
season_wins = sum(unlist(weekly_group_correct_picks))

#calculating the number of people who picked this week
Total = dim(data)[1]

 #Need to fix
# `r paste("CBS Sports win percentage for the week is", CBS, sep = " ") `
```
 `r paste("Our win percentage for the week is", weekly_win_percentage[[length(weekly_win_percentage)]], sep = " ") `
 
 `r paste("Our season win percentage so far is", season_win_percentage, sep = " ") `
 
 `r paste("Games picked this season", season_games, sep = " ") `
 
 `r paste("Correct Games this season", season_wins, sep = " ") `
 
 `r paste(Total, "predictions this week", sep = " ") `
```{r plotting group results, include=FALSE}
#Previous Weeks
group_season_for_plotting = unlist(weekly_win_percentage) %>% as.data.frame() %>% 
  rename(`Win Percentage` = ".") %>% 
  add_column(Week = unlist(weeks))
```

```{r Plotting the group results, echo=FALSE}
group_season_for_plotting %>% 
ggplot(aes(x = as.factor(Week), y = `Win Percentage`))+
  geom_point()+
  geom_path(aes(x = Week))+
  geom_text(aes(label=`Win Percentage`),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  xlab("NFL Week") + 
  ylab("Correct Percentage")+
  ggtitle("Weekly Group Correct Percentage")+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, size = 18))
```

```{r individual results, include=FALSE}
#Creating a list of individual results for each week.
weekly_indiv = pmap(list(inst.picks, winners, weeks), indiv_weekly_pred)

#Combining each week into one dataframe and calculating percentage Correct for this week.  
full_season = weekly_indiv %>% reduce(full_join, by = "Name") %>% 
  mutate(Percent = pull(.[,ncol(.)]/weekly_games_picked[[length(weekly_games_picked)]])) 

#Creating a dataframe with only the weekly picks
a = full_season %>% select(starts_with("Week"))

#Creating a vector of how many weeks each person picked over the season
tot_week = NULL
help = NULL
for (i in 1:dim(a)[1]){
  for(j in 1:length(a)){
    help[j] = ifelse(is.na(a[i,j])==T,0,1)
    tot_week[i] = sum(help)
  }
}

#Creating a vector of how many games each person picked over the season
tot_picks= NULL
help = NULL
for (i in 1:dim(a)[1]){
  for(j in 1:length(a)){
    help[j] = unlist(weekly_games_picked)[j]*ifelse(is.na(a[i,j])==T,0,1)
    tot_picks[i] = sum(help)
  }
}

#Creatign a vector of how many games each person picked correct over the season
tot_correct = NULL
help = NULL
for (i in 1:dim(a)[1]){
  tot_correct[i] = sum(a[i,], na.rm = T)
}

#adding how many weeks each person picked, season correct percentage, and adjusted season percentag to the data frame and sorting the data
indiv_disp = full_season %>% add_column(`Weeks Picked` = tot_week) %>%
  add_column(tot_correct)%>%
  add_column(tot_picks)%>%
  mutate(`Season Percent` = round(tot_correct/tot_picks,4))%>%
  mutate(`Adj Season Percent` = round(`Season Percent`*(tot_week/length(a)),4)) %>%
  select(-tot_correct, -tot_picks) %>%
  arrange(desc(Percent), desc(`Season Percent`)) %>%
  mutate(Percent = ifelse(is.na(Percent)==T, 0, Percent))
```


```{r Printing Individual Table, echo=FALSE}
# Printing the individual Table
indiv_disp %>% gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("Individual Results"),
    subtitle = md(glue("Week {length(weeks)}"))
    ) %>% 
   tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(Percent),
      rows = Percent<.5
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(Percent),
      rows = Percent>.5
    )) %>% 
     tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(`Season Percent`),
      rows = `Season Percent`<.5
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(`Season Percent`),
      rows = `Season Percent`>.5
    ))%>% 
     tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(`Adj Season Percent`),
      rows = `Adj Season Percent`<.5
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(`Adj Season Percent`),
      rows = `Adj Season Percent`>.5
    )) %>% 
  tab_options(
    data_row.padding = px(3)
   ) %>% 
    tab_spanner(
    label = "Weekly # Correct",
    columns = starts_with(c("Week "))
  )

#below may not work if a tie
```
 `r paste("Congrats",indiv_disp$Name[which(indiv_disp$Percent == max(indiv_disp$Percent))],"for having the best picks this week, with a correct percentage of", max(indiv_disp$Percent), sep = " ") `


## Individual Predictions

```{r individual percentages, include=FALSE}
#Calculating individual percentages for each week.
weekly_indiv_percent = map2(weekly_indiv, weekly_games_picked, indiv_percent) %>% reduce(full_join, by = "Name")
```

```{r Plotting individual results over the season, echo=FALSE, out.width = "100%"}
#Creating the individual plot.  
weekly_indiv_percent %>% 
  pivot_longer(cols = starts_with("Week"), names_to = "Week", values_to = "Percent") %>% 
  mutate(Percent = ifelse(is.na(Percent)==T, 0, Percent)) %>% 
  #group_by(Name) %>% 
  ggplot(aes(x = as.factor(Week), y = Percent, color = Name))+
  geom_point()+
  geom_line(aes(x = as.factor(Week), y = Percent, color = Name, 
                group = Name))+
  geom_text_repel(aes(label=Name),hjust=0, vjust=0, size = 3)+
  #geom_text(aes(label=Percent),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week", 
       y = "Correct Percentage", 
       title = "Weekly Individual Correct Percentage")+
  theme_classic()+
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 18))
```

```{r Plotting individual results over the season2, echo=FALSE, out.width = "100%"}
#Creating the individual plot.  
weekly_indiv_percent %>% 
  pivot_longer(cols = starts_with("Week"), names_to = "Week", values_to = "Percent") %>% 
  mutate(Percent = ifelse(is.na(Percent)==T, 0, Percent)) %>% 
  #group_by(Name) %>% 
  ggplot(aes(x = as.factor(Week), y = Percent, color = Name))+
  geom_point()+
  geom_line(aes(x = as.factor(Week), y = Percent, color = Name, 
                group = Name))+
  geom_text_repel(aes(label=round(Percent,4)),hjust=0.5, vjust=2, size = 3)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week", 
       y = "Correct Percentage", 
       title = "Weekly Individual Correct Percentage")+
  facet_wrap(~Name)+
  theme_classic()+
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, size = 18))
```

## MA206 Group Predictions

```{r Cadet Group Predictions, include=FALSE}
#Creating the list of everyones predictions each week.
c_games = map(cdt.picks, games_fn)

#Creating the prediction table.  
c_pred_table = map(c_games, pred_table_fn)

#Adding who won to the predictions
c_with_winners = map2(c_pred_table, winners, adding_winners)

#Creating results for each week.
c_results = map2(c_with_winners,weekly_number_of_games, c_results_fn)
```

```{r Printing Cadet Group Prediction Table, echo=FALSE}
#Displaying the group results
c_results[[length(c_results)]] %>% gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("This Week's MA206 Predictions"),
    subtitle = md(glue("Week {length(results)}"))
    ) %>% 
   tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="No"
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="Yes"
    ))%>% 
  tab_options(
    data_row.padding = px(3)
   )
```


```{r Cadet Weekly and season Group Results, include=FALSE}
# Printing the weekly and season win percentage     

#how many games correct, incorrect, and not picked each week
c_weekly_group_correct = map(c_results, weekly_group_correct_fn)  

#how many games were picked each week
c_weekly_games_picked = map2(c_weekly_group_correct, weekly_number_of_games, weekly_games_picked_fn)

#Calculating the number of correct picks for each week
c_weekly_group_correct_picks = map(c_weekly_group_correct, weekly_group_correct_picks_fn)

#Calculating weekly win percentage
c_weekly_win_percentage = map2(c_weekly_group_correct_picks, c_weekly_games_picked, weekly_win_percentage_fn)

#Calculating season win percentage
c_season_win_percentage = round(sum(unlist(c_weekly_group_correct_picks))/sum(unlist(c_weekly_games_picked)),4)

#Calculating number of games picked this season
c_season_games = sum(unlist(c_weekly_games_picked))

#calculating season wins
season_wins = sum(unlist(weekly_group_correct_picks))
```

```{r Data for MA206 group results, include=FALSE}
#Previous Weeks
c_group_season_for_plotting = unlist(c_weekly_win_percentage) %>% as.data.frame() %>% 
  rename(`Win Percentage` = ".") %>% 
  add_column(Week = unlist(weeks))
```

```{r Plotting MA206 group results, echo=FALSE}
c_group_season_for_plotting %>% 
ggplot(aes(x = as.factor(Week), y = `Win Percentage`))+
  geom_point()+
  geom_path(aes(x = Week))+
  geom_text(aes(label=`Win Percentage`),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week", 
       y = "Correct Percentage", 
       title = "Weekly MA206 Group Correct Percentage", 
       caption = glue::glue("Best week is Week {c_group_season_for_plotting$Week[which(c_group_season_for_plotting$`Win Percentage`==max(c_group_season_for_plotting$`Win Percentage`))]}"))+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, size = 18))
```

## Combined cadet and instructor prediction
```{r Combined Cadet and Instructor Predictions, include=FALSE}
#Combining inst and cadet picks
comb_picks = map2(inst.picks, cdt.picks, comb_picks_fn)

#Creating the list of Combined predictions each week.
comb_games = map(comb_picks, games_fn)

#Creating the Combined prediction table.  
comb_pred_table = map(comb_games, pred_table_fn)

#Adding who won to the predictions
comb_with_winners = map2(comb_pred_table, winners, adding_winners)

#Creating Combined results for each week.
comb_results = map2(comb_with_winners,weekly_number_of_games, comb_results_fn)
```

```{r Printing Combined Prediction Results, echo=FALSE}
#Displaying the Combined results

comb_results[[length(comb_results)]] %>% gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("This Week's Combined Cadet and Instructor Predictions"),
    subtitle = md(glue("Week {length(results)}"))
    ) %>% 
   tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="No"
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="Yes"
    ))%>% 
  tab_options(
    data_row.padding = px(3)
   )
```

```{r Combined Results over season, include=FALSE}
#how many games correct, incorrect, and not picked each week
comb_weekly_group_correct = map(comb_results, weekly_group_correct_fn)  

#how many games were picked each week
comb_weekly_games_picked = map2(comb_weekly_group_correct, weekly_number_of_games, weekly_games_picked_fn)

#Calculating the number of correct picks for each week
comb_weekly_group_correct_picks = map(comb_weekly_group_correct, weekly_group_correct_picks_fn)

#Calculating weekly win percentage
comb_weekly_win_percentage = map2(comb_weekly_group_correct_picks, weekly_games_picked, weekly_win_percentage_fn)

#Calculating season win percentage
comb_season_win_percentage = round(sum(unlist(comb_weekly_group_correct_picks))/sum(unlist(weekly_games_picked)),4)

#Calculating number of games picked this season
comb_season_games = sum(unlist(comb_weekly_games_picked))

#calculating season wins
comb_season_wins = sum(unlist(comb_weekly_group_correct_picks))

# #calculating combined weekly win percentage
# comb_weekly_win_percentage = map2(weekly_group_correct_picks, weekly_games_picked, weekly_win_percentage_fn)

#calculating the number of people who picked this week
comb_Total = dim(comb_picks[[length(comb_picks)]])[1]

comb_season_for_plotting = unlist(comb_weekly_win_percentage) %>% as.data.frame() %>% 
  rename(`Win Percentage` = ".") %>% 
  add_column(Week = unlist(weeks))
```

```{r Plotting the Combined group results, echo=FALSE}
comb_season_for_plotting %>% 
ggplot(aes(x = as.factor(Week), y = `Win Percentage`))+
  geom_point()+
  geom_path(aes(x = Week))+
  geom_text(aes(label=`Win Percentage`),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week", 
       y = "Correct Percentage", 
       title = "Weekly Combined Correct Percentage", 
       caption = glue::glue("Best week is Week {comb_season_for_plotting$Week[which(comb_season_for_plotting$`Win Percentage`==max(comb_season_for_plotting$`Win Percentage`))]}"))+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, size = 18))
```

 `r paste("Our combined win percentage for the week is", comb_weekly_win_percentage[[length(comb_weekly_win_percentage)]], sep = " ") `
 
 `r paste("Our season combined win percentage so far is", comb_season_win_percentage, sep = " ") `
 
 `r paste(comb_Total, "total predictions this week", sep = " ") `
 

```{r matched picks, include=FALSE}
#Finding where inst and Cadet predictions match
matched = map2(results, c_results, matched_fn)
```

```{r Printing matched results, echo=FALSE}
matched[[length(matched)]] %>% gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("This Week's Matched Cadet and Instructor Predictions"),
    subtitle = md(glue("Week {length(results)}"))
    ) %>% 
   tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="No"
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(Correct),
      rows = Correct =="Yes"
    ))%>% 
  tab_options(
    data_row.padding = px(3)
   )
```

```{r include=FALSE}
matched_per = map(matched, matched_percent_fn) %>% unlist() %>% as.data.frame() 

matched_season_percent_for_plotting = matched_per %>% 
  mutate(`Win Percentage` = matched_per[,1]) %>% 
  select(`Win Percentage`) %>% 
  add_column(Week = unlist(weeks)) 
```

```{r Plotting matched percent, echo=FALSE}
matched_season_percent_for_plotting %>% 
  ggplot(aes(x = as.factor(Week), y = `Win Percentage`))+
  geom_point()+
  geom_path(aes(x = Week))+
  geom_text(aes(label=`Win Percentage`),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week", 
       y = "Correct Percentage", 
       title = "Weekly Matched Correct Percentage", 
       caption = glue::glue("Best week is Week {comb_season_for_plotting$Week[which(comb_season_for_plotting$`Win Percentage`==max(comb_season_for_plotting$`Win Percentage`))]}"))+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5, size = 18))
```

`r paste("Our matched win percentage for the week is", matched_per$Percent[length(matched_per$Percent)], sep = " ") `

# Cadet Individual Results
```{r cdt individual results, include=FALSE}
#Creating a list of individual results for each week.
c_weekly_indiv = pmap(list(cdt.picks, winners, weeks), indiv_weekly_pred)

#Combining each week into one dataframe and calculating percentage Correct for this week.  
c_full_season = c_weekly_indiv %>% reduce(full_join, by = "Name") %>% 
  mutate(Percent = pull(.[,ncol(.)]/weekly_games_picked[[length(weekly_games_picked)]])) 

#Creating a dataframe with only the weekly picks
c_a = c_full_season %>% select(starts_with("Week"))

#Creating a vector of how many weeks each person picked over the season
c_tot_week = NULL
c_help = NULL
for (i in 1:dim(c_a)[1]){
  for(j in 1:length(c_a)){
    c_help[j] = ifelse(is.na(c_a[i,j])==T,0,1)
    c_tot_week[i] = sum(c_help)
  }
}

#Creating a vector of how many games each person picked over the season
c_tot_picks= NULL
c_help = NULL
for (i in 1:dim(c_a)[1]){
  for(j in 1:length(c_a)){
    c_help[j] = unlist(weekly_games_picked)[j]*ifelse(is.na(c_a[i,j])==T,0,1)
    c_tot_picks[i] = sum(c_help)
  }
}

#Creatign a vector of how many games each person picked correct over the season
c_tot_correct = NULL
c_help = NULL
for (i in 1:dim(c_a)[1]){
  c_tot_correct[i] = sum(c_a[i,], na.rm = T)
}

#adding how many weeks each person picked, season correct percentage, and adjusted season percentag to the data frame and sorting the data
c_indiv_disp = c_full_season %>% 
  add_column(`Weeks Picked` = c_tot_week) %>%
  add_column(c_tot_correct)%>%
  add_column(c_tot_picks)%>%
  mutate(`Season Percent` = round(c_tot_correct/c_tot_picks,4))%>%
  mutate(`Adj Season Percent` = round(`Season Percent`*(c_tot_week/length(c_a)),4)) %>%
  select(-c_tot_correct, -c_tot_picks) %>%
  arrange(desc(Percent), desc(`Season Percent`)) %>%
  mutate(Percent = ifelse(is.na(Percent)==T, 0, Percent))
```


```{r Printing Individual Cdt Table, echo=FALSE}
# Printing the individual Table
c_indiv_disp %>% gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("MA206 Individual Results"),
    subtitle = md(glue("Week {length(weeks)}"))
    ) %>% 
   tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(Percent),
      rows = Percent<.5
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(Percent),
      rows = Percent>.5
    )) %>% 
     tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(`Season Percent`),
      rows = `Season Percent`<.5
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(`Season Percent`),
      rows = `Season Percent`>.5
    ))%>% 
     tab_style(
    style = cell_text(color = "red", weight = "bold"),
    locations = cells_body(
      columns = vars(`Adj Season Percent`),
      rows = `Adj Season Percent`<.5
    )) %>% 
   tab_style(
    style = cell_text(color = "green", weight = "bold"),
    locations = cells_body(
      columns = vars(`Adj Season Percent`),
      rows = `Adj Season Percent`>.5
    ))%>% 
  tab_options(
    data_row.padding = px(3)
   )%>% 
    tab_spanner(
    label = "Weekly # Correct",
    columns = starts_with(c("Week "))
  )
#below may not work if a tie
```
 `r paste("Congrats",c_indiv_disp$Name[which(c_indiv_disp$Percent == max(c_indiv_disp$Percent))],"for having the best cadet picks this week, with a correct percentage of", max(c_indiv_disp$Percent), sep = " ") `


```{r cdt individual percentages, include=FALSE}
#Calculating  individual percentages for each week.
c_weekly_indiv_percent = map2(c_weekly_indiv, weekly_games_picked, indiv_percent) %>% reduce(full_join, by = "Name")
```

```{r Plotting individual Cdt results over the season, echo=FALSE}
#Creating the individual plot.  
c_weekly_indiv_percent %>% 
  pivot_longer(cols = starts_with("Week"), names_to = "Week", values_to = "Percent") %>% 
  mutate(Percent = ifelse(is.na(Percent)==T, 0, Percent)) %>% 
  #group_by(Name) %>% 
  ggplot(aes(x = as.factor(Week), y = Percent, color = Name))+
  geom_point()+
  geom_line(aes(x = as.factor(Week), y = Percent, color = Name, 
                group = Name))+
  geom_text_repel(aes(label=Name),hjust=0, vjust=0, size = 3)+
  #geom_text(aes(label=Percent),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week",
       y = "Correct Percentage", 
       title = "Weekly MA206 Individual Correct Percentage")+
  theme_classic()+
  theme(legend.position = "none",
    plot.title = element_text(hjust = 0.5, size = 18))
```

```{r Plotting individual Cdt results over the season2, echo=FALSE}
#Creating the individual plot.  
c_weekly_indiv_percent %>% 
  pivot_longer(cols = starts_with("Week"), names_to = "Week", values_to = "Percent") %>% 
  mutate(Percent = ifelse(is.na(Percent)==T, 0, Percent)) %>% 
  #group_by(Name) %>% 
  ggplot(aes(x = as.factor(Week), y = Percent, color = Name))+
  geom_point()+
  geom_line(aes(x = as.factor(Week), y = Percent, color = Name, 
                group = Name))+
  geom_text_repel(aes(label=round(Percent,4)),hjust=.5, vjust=2, size = 3)+
  #geom_text(aes(label=Percent),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week",
       y = "Correct Percentage", 
       title = "Weekly MA206 Individual Correct Percentage")+
  theme_classic()+
  facet_wrap(~Name)+
  theme(legend.position = "none",
    plot.title = element_text(hjust = 0.5, size = 18))
```

```{r pregame, eval=FALSE, include=FALSE}
#Predictions for the week

#Creating the list of everyones predictions each week.
games = map(inst.picks, games_fn)

#Creating the prediction table.  
pred_table = map(games, pred_table_fn)

#Printing table of instructor predictions
pred_table[[length(pred_table)]] %>% mutate(Game = row_number()) %>% 
  rename(`Votes For` = votes_for, `Votes Against` = votes_against) %>% 
  gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("This Week's Predictions"),
    subtitle = md(glue("Week {length(weeks)}"))
    ) %>% 
   tab_options(
    data_row.padding = px(3)
   )

#Creating the list of everyones predictions each week.
c_games = map(cdt.picks, games_fn)

#Creating the prediction table.  
c_pred_table = map(c_games, pred_table_fn)

#Printing table of Cadet predictions
c_pred_table[[length(pred_table)]] %>% mutate(Game = row_number()) %>% 
  rename(`Votes For` = votes_for, `Votes Against` = votes_against) %>% 
  gt() %>% 
  cols_align(
    align = "center") %>% 
   tab_header(
    title = md("This Week's Cadet Predictions"),
    subtitle = md(glue("Week {length(weeks)}"))
    ) %>% 
   tab_options(
    data_row.padding = px(3)
   )

```

```{r}
group_season_for_plotting %>% add_column(Picks = "Instructors") %>% 
  rbind(c_group_season_for_plotting %>% add_column(Picks = "Cadets")) %>% 
  rbind(comb_season_for_plotting %>% add_column(Picks = "Combined")) %>% 
  rbind(matched_season_percent_for_plotting %>% add_column(Picks = "Matched")) %>% 
  ggplot(aes(x = as.factor(Week), y = `Win Percentage`, color = Picks))+
  geom_point()+
  geom_path(aes(x = Week))+
  geom_text_repel(aes(label=`Win Percentage`),hjust=0, vjust=0, size = 3)+
  #geom_text(aes(label=`Win Percentage`),hjust=.5, vjust=-1.5)+
  ylim(c(0, 1)) +
  labs(x = "NFL Week", 
       y = "Correct Percentage",
       title = "Weekly Matched Correct Percentage")+
  theme_clean()+
  theme(plot.title = element_text(hjust = 0.5, size = 18),
        legend.position = "right")
```

